Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2022-10-28 analysis/paper/paper.Rmd
Edit for clarity

To help create a good set of data and code that can easily be shared, the use of programming or scripting languages such as R, Julia, SAS or Python enables us scientists to keep very detailed records of what was computationally performed.
This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.
Text files for saving small sets of data are preferable to proprietary file formats.
Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, e.g., comma separated (CSV) or tab separated (TSV) files.
This also helps to ensure that the data are reusable. Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefit.
Two important benefits to mention here are (i) avoiding data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
Databases such as GenBank are preferable for molecular data and ensure data integrity and machine readability.
While databases may offer many advantages such as speed and data integrity, they are also more complex to set up and administer, and so they may not be the best choice for a small data set.

>>>>

To help create a good set of data and code that can easily be shared, the use of programming or scripting languages such as R, Julia, SAS or Python enables us to keep very detailed records of what was computationally performed.
This is as opposed to using software such as spreadsheet programs like Excel, Google Sheets, Numbers, Calc or others which can be used for simple statistical analyses and visualization or other point-and-click software packages that do not enable us to keep an accurate record of the steps taken to import, format, visualize and analyze data.
Text files for saving small sets of data are preferable to proprietary file formats.
Data that are saved in binary formats such as PDF files are difficult to reuse because they are not easily machine readable.
In many cases, data sets are small enough and curated in spreadsheets, which should be saved as a plain text file, e.g., comma separated (CSV) or tab separated (TSV) files.
This also helps to ensure that the data are reusable. Larger data sets may warrant the use of a proper database like lightweight personal databases, e.g., SQLite or DuckDB, larger more robust databases, e.g., MariaDB, PostgreSQL or a specialized database like GenBank which provide users with several benefit.
Two important benefits to mention here are (i) avoiding data redundancy, ensuring no records are duplicated and (ii) data consistency, ensuring that all records in a data set are recorded in the same format for every observation.
Databases such as GenBank are preferable for molecular data and ensure data integrity and machine readability.
While databases may offer many advantages such as speed and data integrity, they are also more complex to set up and administer, and so they may not be the best choice for a small data set.
